\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Improve conclusion

Our experiment did not directly test configuring a proxy or a custom bridge. From observing participants, we suspect they struggle with these tasks.

@@

\section{Conclusion} 
\label{sec:conclusion}
We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor Launcher. We believe that this is because the interface requires users to know technical terms, provides a lot of freedom for error, and does not give proper feedback. Users in heavily censored environments will likely not succeed in connecting to Tor without outside help. We encourage more usability studies on security tools in general as well as other Tor applications, as they have the potential to create user growth, help user retention, and prevent user frustration. Tor Browser version~5.4.5 incorporated  changes based on our work. We also discussed the possibility of automating connections to Tor with its developers, and they are now considering this as future work.

>>>>

Our experiment did not directly test configuring a proxy or a custom bridge. From observing participants, we suspect they also struggle with these tasks.

@@

\section{Conclusion} 
\label{sec:conclusion}
Our usability evaluation of Tor Launcher measured why and how users have a hard time connecting to Tor. We found that users struggle because the interface requires them to know technical terms, provides room for error, and does not give proper feedback. Users in heavily censored environments will likely not succeed in connecting to Tor without outside help. We encourage more usability studies on security tools in general as well as other Tor applications, as they have the potential to create user growth, help user retention, and prevent user frustration. Tor Browser version~5.4.5 incorporated  changes based on our work. We also discussed the possibility of automating connections to Tor with its developers, and they are now considering this as future work.
